---
title: "Checkbox Group"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

```{r, echo=FALSE}

shinyApp(

  ui = fluidPage(
    
    checkboxGroupInput("checkGroup", label = h3("Checkbox Group"), 
                       choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3),
                       selected = 1),
    
    hr(),
    
    fluidRow(column(12, verbatimTextOutput("value")))
    
  ),
  
  server = function(input, output) {
    
    # You can access the values of the widget (as a vector)
    # with input$checkGroup, e.g.
    output$value <- renderPrint({ input$checkGroup })
    
  },

  options = list(height = 350, display.mode = "showcase")
)
```

## Checkbox Group {.tabset}

Creates a group of checkboxes. The widget sends the server a character vector that contains the values of the selected boxes.

**Function**

```{r eval=F, echo=T}
checkboxGroupInput(inputId, label, choices, selected = NULL)
```

**Arguments**

<span style="color: red">inputId</span> The name to use to look up the value of the widget (as a character string)

<span style="color: red">label</span> A label to display above the check boxes

<span style="color: red">choices</span> A list of values. The widget will build a checkbox for each value of the list. If the list has names, these will be displayed next to the checkboxes. Otherwise the values themselves will be displayed.

<span style="color: red">selected</span> The values that should initially be selected, if any.

<br>

### ui.R
```{r, eval=F, echo=T}

fluidPage(
    
  checkboxGroupInput("checkGroup", label = h3("Checkbox Group"), 
    choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3),
    selected = 1),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)
  
```
### server.R
```{r, eval=F, echo=T}

function(input, output) {

  output$value <- renderPrint({ input$checkGroup })
  
})
```
### app.R
```{r, eval=F, echo=T}

ui = fluidPage(
    
  checkboxGroupInput("checkGroup", label = h3("Checkbox Group"), 
    choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3),
    selected = 1),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)

server = function(input, output) {

  output$value <- renderPrint({ input$checkGroup })

}

# Run the application 
shinyApp(ui = ui, server = server)

```
