---
title: "Date Range"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

```{r, echo=FALSE}

shinyApp(

  ui = fluidPage(
    
    dateRangeInput("dates", label = h3("Date Range")),
    
    hr(),
    
    fluidRow(column(12, verbatimTextOutput("value")))
    
  ),
  
  server = function(input, output) {
    
    output$value <- renderPrint({ input$dates })
    
  },

  options = list(height = 350, display.mode = "showcase")
)
```

## Date Range {.tabset}

Creates two text fields that the user can click on to access calendars to select a date range. Sends the result to the server as a vector with two <span style="color: red">Date</span> objects.

**Function**

```{r eval=F, echo=T}
dateRangeInput(inputId, label, start = NULL, end = NULL, min = NULL, max = NULL, format = "yyyy-mm-dd", startview = "month", weekstart = 0, language = "en", separator = " to ")
```

**Arguments**

<span style="color: red">inputId</span> The name to use to look up the value of the widget (as a character string)

<span style="color: red">label</span> A label to display above the text fields

<span style="color: red">start</span> The start date to display. Either a Date object, or a string in yyyy-mm-dd format. If NULL (the default), will use the current date in the client's time zone.

<span style="color: red">end</span> The end date to display. Either a Date object, or a string in yyyy-mm-dd format. If NULL (the default), will use the current date in the client's time zone.

<span style="color: red">separator</span> The string to display between the start and end boxes

<span style="color: red">min</span> The minimum allowed date. Either a Date object, or a string in yyyy-mm-dd format.

<span style="color: red">max</span> The maximum allowed date. Either a Date object, or a string in yyyy-mm-dd format.

<span style="color: red">format</span> The format of the date to display in the browser. Defaults to "yyyy-mm-dd". See the help page for a list of options (?dateInput).

<span style="color: red">startview</span> The date range shown when a text field is first clicked. Can be "month" (the default), "year", or "decade".

<span style="color: red">weekstart</span> Which day is the start of the week. Should be an integer from 0 (Sunday) to 6 (Saturday).

<span style="color: red">language</span> The language used for month and day names. Default is "en" for English. Other valid values include "bg", "ca", "cs", "da", "de", "el", "es", "fi", "fr", "he", "hr", "hu", "id", "is", "it", "ja", "kr", "lt", "lv", "ms", "nb", "nl", "pl", "pt", "pt-BR", "ro", "rs", "rs-latin", "ru", "sk", "sl", "sv", "sw", "th", "tr", "uk", "zh-CN", and "zh-TW".

<br>

### ui.R
```{r, eval=F, echo=T}

fluidPage(
    
  dateRangeInput("dates", label = h3("Date Range")),

  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)
  
```
### server.R
```{r, eval=F, echo=T}

function(input, output) {

  output$value <- renderPrint({ input$dates })
  
})
```
### app.R
```{r, eval=F, echo=T}

ui = fluidPage(
    
  dateRangeInput("dates", label = h3("Date Range")),

  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)

server = function(input, output) {

  output$value <- renderPrint({ input$dates })

}

# Run the application 
shinyApp(ui = ui, server = server)

```
