---
title: "File Input"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

```{r, echo=FALSE}

shinyApp(

  ui = fluidPage(
    
    fileInput("file", label = h3("File Input")),
    
    hr(),
    
    fluidRow(column(12, verbatimTextOutput("value")))
    
  ),
  
  server = function(input, output) {
    
    output$value <- renderPrint({ str(input$file) })
    
  },

  options = list(height = 350, display.mode = "showcase")
)
```

## File Input {.tabset}

Creates a file upload manager that can be used to upload one or more files at once. Does not work on older browsers, including Internet Explorer 9 and earlier.

The file upload widget will pass the server a data frame that contains one row for each file uploaded and four columns:

- <span style="color: red">name</span> The filename provided by the web browser for the file
- <span style="color: red">size</span> The size of the uploaded file in bytes
- <span style="color: red">type</span> The MIME type of the file (as reported by the browser). For example <span style="color: red">text/plain</span> or an empty string (if the browser could not determine the type).
- <span style="color: red">datapath</span> The path to the temp file that contains the data that was uploaded. This file may be deleted if the user performs another upload operation.

**Function**

```{r eval=F, echo=T}
fileInput(inputId, label, multiple = FALSE, accept = NULL)
```

**Arguments**

<span style="color: red">inputId</span> The name to use to look up the value of the widget (as a character string)

<span style="color: red">label</span> A label to display above the widget

<span style="color: red">multiple</span> Whether or not the user should be allowed to upload multiple files at once

<span style="color: red">accept</span> A character vector of MIME types that the browser can expect the uploaded files to be.

<br>

### ui.R
```{r, eval=F, echo=T}

fluidPage(
  
  fileInput("file", label = h3("File Input")),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)
  
```
### server.R
```{r, eval=F, echo=T}

function(input, output) {

  output$value <- renderPrint({ str(input$file) })
  
}
```
### app.R
```{r, eval=F, echo=T}

ui = fluidPage(
    
  fileInput("file", label = h3("File Input")),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)

server = function(input, output) {
  
  output$value <- renderPrint({ str(input$file) })
  
}

# Run the application 
shinyApp(ui = ui, server = server)

```
