---
title: "Numeric Input"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

```{r, echo=FALSE}

shinyApp(

  ui = fluidPage(
    
    numericInput("num", label = h3("Numeric Input"), value = 1),
    
    hr(),
    
    fluidRow(column(12, verbatimTextOutput("value")))
    
  ),
  
  server = function(input, output) {
    
    output$value <- renderPrint({ input$num })
    
  },

  options = list(height = 350, display.mode = "showcase")
)
```

## Numeric Input {.tabset}

Creates a box you can use to enter numeric values. You can type a number or scroll through values with the box's scroll bar. The widget will pass the value shown in the box to the server as a double (e.g. number).

**Function**

```{r eval=F, echo=T}
numericInput(inputId, label, value, min = NA, max = NA, step = NA)
```

**Arguments**

<span style="color: red">inputId</span> The name to use to look up the value of the widget (as a character string)

<span style="color: red">label</span> A label to display above the number field

<span style="color: red">value</span> The initial number to display in the number field

<span style="color: red">min</span> The minimum number that can be selected

<span style="color: red">max</span> The maximum number that can be selected

<span style="color: red">step</span> The amount to increment the value by when a user clicks up or down on the scroll bar.

<br>

### ui.R
```{r, eval=F, echo=T}

fluidPage(
    
    numericInput("num", label = h3("Numeric Input"), value = 1),
    
    hr(),
    
    fluidRow(column(12, verbatimTextOutput("value")))
    
  )
  
```
### server.R
```{r, eval=F, echo=T}

function(input, output) {

  output$value <- renderPrint({ input$num })
  
}
```
### app.R
```{r, eval=F, echo=T}

ui = fluidPage(
    
  numericInput("num", label = h3("Numeric Input"), value = 1),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)

server = function(input, output) {
  
  output$value <- renderPrint({ input$num })
  
}

# Run the application 
shinyApp(ui = ui, server = server)

```
