---
title: "Radio Buttons"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

```{r, echo=FALSE}

shinyApp(

  ui = fluidPage(
    
    radioButtons("radio", label = h3("Radio Buttons"),
                 choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3), 
                 selected = 1),
    
    hr(),
    
    fluidRow(column(12, verbatimTextOutput("value")))
    
  ),
  
  server = function(input, output) {
    
    output$value <- renderPrint({ input$radio })
    
  },

  options = list(height = 350, display.mode = "showcase")
)
```

## Radio Buttons {.tabset}

Creates a set of radio buttons, several buttons only one of which can be pressed at any time. The widget will return the value of the selected button to the server as a character string.

**Function**

```{r eval=F, echo=T}
radioButtons(inputId, label, choices, selected = NULL)
```

**Arguments**

<span style="color: red">inputId</span> The name to use to look up the value of the widget (as a character string)

<span style="color: red">label</span> A label to display above the buttons

<span style="color: red">choices</span> A list of values. The widget will build a button for each value of the list. If the list has names, these will be displayed next to the buttons. Otherwise the values themselves will be displayed.

<span style="color: red">selected</span> The value that should initially be selected, defaults to the first value.

<br>

### ui.R
```{r, eval=F, echo=T}

fluidPage(
  
  radioButtons("radio", label = h3("Radio Buttons"),
    choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3), 
    selected = 1),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)
  
```
### server.R
```{r, eval=F, echo=T}

function(input, output) {

  output$value <- renderPrint({ input$radio })
  
}
```
### app.R
```{r, eval=F, echo=T}

ui = fluidPage(
    
  radioButtons("radio", label = h3("Radio Buttons"),
    choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3), 
    selected = 1),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)

server = function(input, output) {

  output$value <- renderPrint({ input$radio })

}

# Run the application 
shinyApp(ui = ui, server = server)

```
