---
title: "Select Box"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

```{r, echo=FALSE}

shinyApp(

  ui = fluidPage(
    
    selectInput("select", label = h3("Select Box"), 
                choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3), 
                selected = 1),
    
    hr(),
    
    fluidRow(column(12, verbatimTextOutput("value")))
    
  ),
  
  server = function(input, output) {
    
    output$value <- renderPrint({ input$select })
    
  },

  options = list(height = 350, display.mode = "showcase")
)
```

## Select Box {.tabset}

Creates a drop-down list that you can use to select one or more items. The widget will pass the value of the selected items to the server as a vector of character strings (usually of length one).

**Function**

```{r eval=F, echo=T}
selectInput(inputId, label, choices, selected = NULL, multiple = FALSE, selectize = TRUE)
```

**Arguments**

<span style="color: red">inputId</span> The name to use to look up the value of the widget (as a character string)

<span style="color: red">label</span> A label to display above the drop-down box

<span style="color: red">choices</span> A list of values. The widget will include a menu option for each value of the list. If the list has names, these will be displayed in the drop down menu. Otherwise the values themselves will be displayed.

<span style="color: red">selected</span> The value(s) that should initially be selected. Defaults to the first value, or no values if <span style="color: red">multiple = TRUE</span>.

<span style="color: red">multiple TRUE</span> if the user is allowed to select multiple values at once. <span style="color: red">FALSE</span> otherwise.

<span style="color: red">selectize TRUE</span> id Shiny should use selectize.js to build an enriched selection box. <span style="color: red">FALSE</span> if Shiny should build a basic selection box.

<br>

### ui.R
```{r, eval=F, echo=T}

fluidPage(
  
  selectInput("select", label = h3("Select Box"), 
    choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3), 
    selected = 1),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)
  
```
### server.R
```{r, eval=F, echo=T}

function(input, output) {

  output$value <- renderPrint({ input$select })
  
}
```
### app.R
```{r, eval=F, echo=T}

ui = fluidPage(
    
  selectInput("select", label = h3("Select Box"), 
    choices = list("Choice 1" = 1, "Choice 2" = 2, "Choice 3" = 3), 
    selected = 1),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)

server = function(input, output) {

  output$value <- renderPrint({ input$select })

}

# Run the application 
shinyApp(ui = ui, server = server)

```
