---
title: "Single Checkbox"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<br>

```{r, echo=FALSE}

shinyApp(

  ui = fluidPage(
    
    # Copy the line below to make a checkbox
    checkboxInput("checkbox", label = "Choice A", value = TRUE),
    
    hr(),
    
    fluidRow(column(12, verbatimTextOutput("value")))
    
  ),
  
  server = function(input, output) {
    
    # You can access the value of the widget with input$checkbox, e.g.
    output$value <- renderPrint({ input$checkbox })
    
  },

  options = list(height = 350, display.mode = "showcase")
)
```

## Single Checkbox {.tabset}

Creates a single checkbox. The widget sends the server <span style="color: red">TRUE</span> if the box is checked, <span style="color: red">FALSE</span> otherwise.

**Function**

```{r eval=F, echo=T}
checkboxInput(inputId, label, value = FALSE)
```

**Arguments**

<span style="color: red">inputId</span> The name to use to look up the value of the widget (as a character string)

<span style="color: red">label</span> A label to display next to the checkbox

<span style="color: red">value</span> A logical value. If <span style="color: red">TRUE</span>, the checkbox will begin checked. If <span style="color: red">FALSE</span>, it will begin unchecked.

<br>

### ui.R
```{r, eval=F, echo=T}

fluidPage(
  
  checkboxInput("checkbox", label = "Choice A", value = TRUE),
    
  hr(),
  
  fluidRow(column(3, verbatimTextOutput("value")))
  
)
  
```
### server.R
```{r, eval=F, echo=T}

function(input, output) {

  output$value <- renderPrint({ input$checkbox })
  
}
```
### app.R
```{r, eval=F, echo=T}

ui = fluidPage(
    
  checkboxInput("checkbox", label = "Choice A", value = TRUE),
  
  hr(),
  
  fluidRow(column(12, verbatimTextOutput("value")))
  
)

server = function(input, output) {

  output$value <- renderPrint({ input$checkbox })

}

# Run the application 
shinyApp(ui = ui, server = server)

```
